### 2013-05-14 inst/examples/BUGS/allen.Rmd
Updated runs of complete script
* Includes alternative Figure 1 (in time-series space, with GP #44)
* Includes (fixed) Bayesian Ricker (#43) and Bayesian Myers (#42) case

@@

```{r}
OPT = data.frame(GP = opt_gp$D, True = opt_true$D, MLE = opt_estimated$D, Ricker = opt_alt$D, Parametric.Bayes = opt_par_bayes$D, Myers = myers_alt$D)
colorkey=cbPalette
names(colorkey) = names(OPT) 
```

@@

```{r}
model = "MLE"
ggplot(subset(dt, method == model)) + 
  geom_line(aes(time, fishstock, group=interaction(reps,method), color=method), alpha=.1) +
  scale_colour_manual(values=colorkey, guide = guide_legend(override.aes = list(alpha = 1))) +
  ylim(0, 9)
ggsave(paste(model, "_sim.pdf", sep=""), width=6, height=4)

```{r Figure3a}
dt$reps <- as.integer(dt$reps)

require(animation)
ani.options(loop=TRUE)
saveMovie({    
    for (i in seq(1, OptTime, by=2)) {
      print(
        ggplot(subset(dt, method %in% c("True", "Ricker") & reps < 5 & time <= i), 
               aes(time, fishstock, group=interaction(reps,method), color = method), alpha=.9) + 
          geom_line() + xlim(0, OptTime)
        )
    }
}, interval = 0.1, movie.name = "wrong-model.gif", ani.width = 600, ani.height = 600)

require(MASS)
s <- length(gp_dat$Cf_posterior)

# Samples from the posterior of GPs
draws <- sapply(1:s, function(i)
  mvrnorm(1, gp_dat$Ef_posterior[,i], gp_dat$Cf_posterior[[i]]))
draws <- melt(data.frame(x=x_grid, draws), id="x")

## Samples from the expected GP
gp_draws <- mvrnorm(6, gp_dat$E_Ef, gp_dat$E_Cf)
gp_draws <- melt(data.frame(x=x_grid, t(gp_draws)), id="x")

ggplot(tgp_dat) + geom_ribbon(aes(x,y,ymin=ymin,ymax=ymax), fill="gray80") +
  geom_line(aes(x,y,ymin=ymin,ymax=ymax)) +
  # geom_line(data=gp_draws, aes(x=x, y=value, col=variable))  +  
  geom_line(data=draws, aes(x=x, y=value, index=variable), alpha=.1)

@@

```{r totalprofits}
ggplot(Profit, aes(V1)) + geom_histogram() + 
  facet_wrap(~method, scales = "free_y") + guides(legend.position = "none")
```

>>>>

##

```{r step_ahead}
gp_f_at_obs <- gp_predict(gp, x, burnin=1e4, thin=300)

step_ahead <- function(x, f, p){
  h = 0
  x_predict <- sapply(x, f, h, p)
  n <- length(x_predict) - 1
  y <- c(x[1], x_predict[1:n])
  y
}

df <- melt(data.frame(time = 1:length(x), stock = x, 
                GP = gp_f_at_obs$E_Ef,
                True = step_ahead(x,f,p),  
                MLE = step_ahead(x,f,est$p), 
                Parametric.Bayes = step_ahead(x, f, bayes_pars), 
                Ricker = step_ahead(x,alt$f, ricker_bayes_pars), 
                Myers = step_ahead(x, Myer_harvest, myers_bayes_pars)
                 ), id=c("time", "stock"))

ggplot(df) + geom_point(aes(time, stock)) + 
  geom_line(aes(time, value, col=variable)) +
    scale_colour_manual(values=colorkey) 
```

@@

```{r}
OPT = data.frame(opt_gp$D, opt_true$D, opt_estimated$D, opt_alt$D, opt_par_bayes$D, myers_alt$D)

names(OPT) = names(colorkey)[1:6]
```

@@

@@

```{r totalprofits}
ggplot(Profit, aes(V1)) + geom_histogram() + 
  facet_wrap(~method, scales = "free_y") + guides(legend.position = "none") + xlab("Total profit by replicate")
```
